Figures compiler

### 2017-12-06 analyses/figures-compiler.Rmd
figures done

## Plot all minimum ages
multi.plot.max.min(data_list_max, what = c("age"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

## Plot all minimum disparity
multi.plot.max.min(data_list_max, what = c("disparity"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

>>>>

## Plot all minimum ages
multi.plot.max.min(data_list_min, what = c("age"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

## Plot all minimum disparity
multi.plot.max.min(data_list_min, what = c("disparity"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))
